Proportional multi-state multiple-cohort life table model

### 2018-04-20 MSLT/MSLTdoc.Rmd
Modify age groups for cohort simulation

6) Create age categories index in GBDdata (upper limit age group to match injury data), total of 20 age groups. These are the age cohorts to simulate. 
```{r, echo=TRUE}
GBDdata$age_cat [GBDdata$age =="under 5"] <- 5
GBDdata$age_cat [GBDdata$age =="5 to 9"] <- 10
GBDdata$age_cat [GBDdata$age =="10 to 14"] <- 15
GBDdata$age_cat [GBDdata$age =="15 to 19"] <- 20
GBDdata$age_cat [GBDdata$age =="20 to 24"] <- 25
GBDdata$age_cat [GBDdata$age =="25 to 29"] <- 30
GBDdata$age_cat [GBDdata$age =="30 to 34"] <- 35
GBDdata$age_cat [GBDdata$age =="35 to 39"] <- 40
GBDdata$age_cat [GBDdata$age =="40 to 44"] <- 45
GBDdata$age_cat [GBDdata$age =="45 to 49"] <- 50
GBDdata$age_cat [GBDdata$age =="50 to 54"] <- 55
GBDdata$age_cat [GBDdata$age =="55 to 59"] <- 60
GBDdata$age_cat [GBDdata$age =="60 to 64"] <- 65
GBDdata$age_cat [GBDdata$age =="65 to 69"] <- 70
GBDdata$age_cat [GBDdata$age =="70 to 74"] <- 75
GBDdata$age_cat [GBDdata$age =="75 to 79"] <- 80
GBDdata$age_cat [GBDdata$age =="80 to 84"] <- 85
GBDdata$age_cat [GBDdata$age =="85 to 89"] <- 90
GBDdata$age_cat [GBDdata$age =="90 to 94"] <- 95
GBDdata$age_cat [GBDdata$age =="95 plus"] <- 100
```

>>>>

6) Create age categories index in GBDdata (mid age, to match cohort running), total of 20 age groups. These are the age cohorts to simulate. 
```{r, echo=TRUE}
# 22, 27, 32, 37, 42, 47, 52, 57, 62, 67, 72, 77, 82, 87, 92, 97
GBDdata$age_cat [GBDdata$age =="under 5"] <- 2
GBDdata$age_cat [GBDdata$age =="5 to 9"] <- 7
GBDdata$age_cat [GBDdata$age =="10 to 14"] <- 12
GBDdata$age_cat [GBDdata$age =="15 to 19"] <- 17
GBDdata$age_cat [GBDdata$age =="20 to 24"] <- 22
GBDdata$age_cat [GBDdata$age =="25 to 29"] <- 27
GBDdata$age_cat [GBDdata$age =="30 to 34"] <- 32
GBDdata$age_cat [GBDdata$age =="35 to 39"] <- 37
GBDdata$age_cat [GBDdata$age =="40 to 44"] <- 42
GBDdata$age_cat [GBDdata$age =="45 to 49"] <- 47
GBDdata$age_cat [GBDdata$age =="50 to 54"] <- 52
GBDdata$age_cat [GBDdata$age =="55 to 59"] <- 57
GBDdata$age_cat [GBDdata$age =="60 to 64"] <- 62
GBDdata$age_cat [GBDdata$age =="65 to 69"] <- 67
GBDdata$age_cat [GBDdata$age =="70 to 74"] <- 72
GBDdata$age_cat [GBDdata$age =="75 to 79"] <- 77
GBDdata$age_cat [GBDdata$age =="80 to 84"] <- 82
GBDdata$age_cat [GBDdata$age =="85 to 89"] <- 87
GBDdata$age_cat [GBDdata$age =="90 to 94"] <- 92
GBDdata$age_cat [GBDdata$age =="95 plus"] <- 97
```
